Pipit on the Post: Proving Pre- and Post-conditions of Reactive Systems

### 2024-01-18 2024pipit/section/60-Evaluation.tex
update evaluation

We were able to verify the Kind2 implementation of the simplified trigger-fetch mechanism for trigger arrays containing up to 16 elements; above that, a 32-size array reported multiple runtime errors and did not terminate after several hours.
% Verification of a 4-size array took 11s of CPU time; an 8-size array took 13s; a 16-size array took 276s; and a 32-size array timed out after several hours and multiple runtime errors.
For reference, the M_TTCAN hardware implementation of TTCAN supports up to 64 triggers~\cite{bosch2019mttcan}.

@@

\autoref{f:evaluation:kind2-runtime} shows the verification runtime for different sizes of arrays; the Pipit version is parametric in the array size, and is thus verified for all sizes of arrays.
We ran these experiments on a 2020 M1 MacBook Air with 16 gigabytes of RAM.
Both Kind2 and Pipit developments of the simplified trigger-fetch logic are roughly the same size, on the order of two-hundred lines of code including comments.

\begin{figure}
  \center
\begin{tabular}{r|rr|rr|rr}
  & \multicolumn{4}{c|}{Kind2} & Pipit \\
  & \multicolumn{2}{c|}{simple enable-set} & \multicolumn{2}{c|}{full enable-set} & \\
  size & wall-clock & CPU & wall-clock & CPU & wall-clock & CPU \\
  \hline
  1 & 2s &  3s  & 6s & 12s & 6s & 6s \\
  2 & 3s &  3s  & 8s & 12s & 6s & 6s \\
  4 & 5s & 11s  & 12s & 24s & 6s & 6s \\
  8 & 8s & 13s  & 82s & 90s & 6s & 6s \\
  16 & 125s & 276s & \multicolumn{2}{c|}{error} & 6s & 6s \\
  32 & \multicolumn{2}{c|}{error} & \multicolumn{2}{c|}{error} & 6s & 6s \\
\end{tabular}
\caption{Verification time for trigger-fetch; simple enable-set uses a simplified version of the enable-set, while full enable-set uses bitwise arithmetic as in the TTCAN specification. The verification time for Pipit is a once-and-for-all proof that is parametric in the size of the array.}
\label{f:evaluation:kind2-runtime}
\end{figure}

>>>>

We were able to reliably verify the Kind2 implementation of the simplified trigger-fetch mechanism for trigger arrays containing up to 16 elements; above that, we ran into intermittent runtime errors.
% Verification of a 4-size array took 11s of CPU time; an 8-size array took 13s; a 16-size array took 276s; and a 32-size array timed out after several hours and multiple runtime errors.
For reference, the M_TTCAN hardware implementation of TTCAN supports up to 64 triggers~\cite{bosch2019mttcan}.

@@

\autoref{f:evaluation:kind2-runtime} shows the verification runtime for different sizes of arrays; the Pipit version is parametric in the array size, and is thus verified for all sizes of arrays.
We ran these experiments in Docker on an Intel i5-12500 with 32GB of RAM.
Both Kind2 and Pipit developments of the simplified trigger-fetch logic are roughly the same size, on the order of two-hundred lines of code including comments.

\begin{figure}
  \center
\begin{tabular}{r|rr|rr|rr}
  & \multicolumn{4}{c|}{Kind2} & Pipit \\
  & \multicolumn{2}{c|}{simple enable-set} & \multicolumn{2}{c|}{full enable-set} & \\
  size & wall-clock & user-time & wall-clock & user-time & wall-clock & user-time \\
  \hline

  1 & 1.51s&1.33s
  & 1.61s&2.26s
  & 5.28s&5.03s \\
  2 & 1.50s&1.29s
  & 1.68s&2.85s
  & 5.28s&5.03s \\
  4 & 1.56s&1.59s
  & 2.10s&5.05s
  & 5.28s&5.03s \\
  8 & 1.80s&3.12s
  & 4.29s&18.12s
  & 5.28s&5.03s \\
  16 & 3.41s&12.29s
  & 16.41s&71.23s
  & 5.28s&5.03s \\
  32 & 11.24s&67.27s
  & 941.64s&3853.16s
  & 5.28s&5.03s \\
\end{tabular}
\caption{Verification time for trigger-fetch; simple enable-set uses a simplified version of the enable-set, while full enable-set uses bitwise arithmetic as in the TTCAN specification. The verification time for Pipit is a once-and-for-all proof that is parametric in the size of the array. We were unable to verify arrays of size 64 with Kind2 as our verification timed out after three hours.}
\label{f:evaluation:kind2-runtime}
\end{figure}
